---
title: "Part b of the exercise 1"
author: "Ahmadreza Yousefkhani"
date: "9/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description
Create an HTML document that samples 100 values from a log-normal distribution (say, $\mu=1, \sigma=.25$); create a histogram of the distribution and the distribution on the log scale; report the mean and variance of the sample in line in the text. 

## Solution
First, I am going to sample the values from a log-normal. As the standard deviation cannot be negative, I am considering that the values given in the question are in the log scale:
```{r}
samp <- rlnorm(n = 100, meanlog = 1 , sdlog = 0.25)
```

Now plotting the histogram of the samples:
```{r}
hist(samp, breaks = 20, main = "Histogram of 100 log-normals")
```

Plotting the histogram of the distribution on the log-scale:
```{r}
hist(log(samp), breaks = 20, main = "Histogram of 100 log-normals")
```

The sample mean is `r mean(samp)` and the sample variance is `r var(samp)`.
This was the end of this exercise!

